Democracy, Public Support, and Measurement Uncertainty

### 2021-06-06 paper/dcpo_demsupport.Rmd
use theta_dem_trim and theta_aut_trim in dcpo ajps models and cls ajps models. The previous ones also usded trimmed data but named as "theta_dem" and theta_aut". @sammo3182.

source(here("R", "tidy_pgmm.r"))
source(here("R", "moc_function.R")) 
source(here("R", "moc_summary.R"))

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

@@

supdem <- read.csv("../data/Support_democracy_ajps.csv")
v_dem <- read.csv("../data/vdem15.csv")
sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here("data", "claassen_m5_theta.rda"))
load(here("data", "dem_mood_apsr.RData"))
load(here("data", "dcpo_input.rda"))
load(here("data", "dcpo_theta.rda"))
load(here("data", "dcpo_sigma.rda"))
load(here("data", "dcpo_ajps_rubin.rda"))

## Beck-Katz panel-corrected standard errors
vcovBK_se <- function(x) {
  plm::vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

vcovHC_se <-  function(x) {
  plm::vcovHC(x, method="arellano", cluster="group") %>%  #default setting
    diag() %>% 
    sqrt()
}

reformat_dcpo_output <- function(x, parameter_name) {
  df_temp <- x %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = parameter_name) %>%
    arrange(country, year)
  return(df_temp)
}
```

@@

```{r dcpo_input_raw}
dcpo_input_raw <-
  DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
                                        col_types = "cccccc"),
                        file = "data/dcpo_input_raw.csv")
```

```{r dcpo_input, eval=TRUE}
dcpo_input_raw1 <-
  read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>%
  filter(!(
    str_detect(survey, "army_wvs") &
      # WVS obs identified as problematic by Claassen
      ((country == "Albania" & year == 1998) |
         (country == "Indonesia" &
            (year == 2001 | year == 2006)) |
         (country == "Iran" & year == 2000) |
         (country == "Pakistan" &
            (year == 1997 | year == 2001)) | # 1996 in Claassen
         (country == "Vietnam" & year == 2001)
      ) |
      (str_detect(item, "strong_wvs") &
         ((country == "Egypt" & year == 2012) |
            (country == "Iran" &
               (year == 2000 | year == 2007)) | # 2005 in Claassen
            (country == "India") |
            (country == "Pakistan" &
               (year == 1997 | year == 2001)) | # 1996 in Claassen
            (country == "Kyrgyzstan" &
               (year == 2003 | year == 2011)) |
            (country == "Romania" &
               (year == 1998 | year == 2005 | year == 2012)) |
            (country == "Vietnam" & year == 2001)
         )) |
      (
        country %in% c(
          "Puerto Rico",
          "Northern Ireland",
          "SrpSka Republic",
          "Hong Kong SAR China"
        )
      )
  )) %>%
  with_min_yrs(2)

dcpo_input <- DCPOtools::format_dcpo(dcpo_input_raw1,
                                     scale_q = "church_lb",
                                     scale_cp = 2)
save(dcpo_input, file = here::here("data", "dcpo_input.rda"))
```

```{r compare_n, eval=TRUE}
# if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
#   dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
#     read_csv(col_types = "cdcddcdc") %>% 
#     write_csv("data/supdem raw survey marginals.tab")
# }

@@

```{r dcpo}
iter <- 3000

dcpo_output <- dcpo(dcpo_input,
                    iter = iter,
                    chains = 4,
                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))

save(dcpo_output, file = here::here("data", "dcpo_output.rda"))

dcpo_theta <- rstan::extract(dcpo_output, pars = "theta")

save(dcpo_theta, file = here::here("data", "dcpo_theta.rda"))

dcpo_sigma <- rstan::extract(dcpo_output, pars = "sigma")

save(dcpo_sigma, file = here::here("data", "dcpo_sigma.rda"))

dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")

save(dcpo_input, dcpo_y_r_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
```

```{r country-years}
path_df <-
  list.files(
    "../data",
    pattern = ".*_theta.rda",
    recursive = TRUE,
    full.names = TRUE
  ) %>%
  .[str_which(., "claassen")]

load(path_df)

df_thetaDraw <- map_df(seq(claassen_m5_theta$theta[1, , 1]),
       function(year) {
         map_df(seq(claassen_m5_theta$theta[1, 1, ]),
                function(country) {
                  df_temp <-
                    sample(claassen_m5_theta$theta[, year, country],
                           size = 100,
                           replace = TRUE) %>%
                    matrix(ncol = 100) %>%
                    as_tibble()
                  df_temp$yearID <- year
                  df_temp$countryID <- country
                  return(df_temp)
                })
       }) %>% 
  pivot_longer(
    cols = starts_with("V"),
    names_to = "draw",
    values_to = "theta"
  ) %>% 
  group_split(draw)
```

@@

```{r claassenAJPS, eval=TRUE}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

```{r claassenUncertaintyAJPS}
ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

df_cls <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
    #           by = c("year", "country")) %>%
    left_join(sd_control, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

result_clsUncertain <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r dcpoMean}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>%
    reformat_dcpo_output("theta") %>%
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country"))
}) %>%
  group_by(country, year) %>%
  summarise(theta = mean(theta),
            sigma = mean(sigma))

saveRDS(df_dcpoMean, file = here("data", "df_dcpoMean.RDS"))
```

```{r dcpoPointAJPS}
df_controls <- readRDS(here("data", "control_variables_ajps.rds")) %>% 
  mutate(country = countrycode::countrycode(country, "country.name", "country.name"),
         regime = Vdem_regime > 1) %>% 
  filter(year >= first_year) # using trimmed data as Claassen

df_dcpoMeanAJPS <- df_dcpoMean %>% 
  right_join(df_controls, by = c("country", "year")) %>% 
  mutate(theta_dem = theta * regime,
         theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))

@@

ls_mod <- c(
  glue("plm({ls_eq}, model = 'pooling', data = df_dcpoMeanAJPS)"),
  glue(
    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = df_dcpoMeanAJPS, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
  )
)

#There's a problem to run this part---------------------

df_result_dcpo <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))
})

tidy_dcpo <- map(df_result_dcpo, function(result) {
  df_result <- tidy(result, conf.int = TRUE)

glance_dcpo <- map(df_result_dcpo, function(aResult){
  if(class(aResult) == "plm"){ 
    glance.plm(aResult) # using the customized glance function
  }else{
      glance(aResult)
    }
})

result_dcpo <- map2(tidy_dcpo, glance_dcpo, ~ list(.x, .y))
names(result_dcpo) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_dcpo, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
```

```{r dcpoUncertaintyAJPS}
df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
  .x[[.y]] %>%
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>%
    plm::pdata.frame(index = c("country", "year"))
}) # The code is to fit the embedded format of dcpo_ajps_rubin

ls_mod <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
    )
)

result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
  mod_eval <- function(aData) eval(parse(text = aMod))

@@

```{r visualizeAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}

```{r visualizedUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty"}

@@

```{r claassenAPSR, eval = TRUE}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

```{r claassenAPSRUncertainty}
ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

@@

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = aData)")
)

result_clsUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r dcpoPointAPSR}

df_dcpoMean <- readRDS(here("data", "df_dcpoMean.RDS"))

df_controls <- readRDS(here("data", "control_variables_apsr.rds")) %>% 
  mutate(country = countrycode::countrycode(country, "country.name", "country.name")) %>% 
  filter(year >= first_year)

df_dcpoMeanAPSR <- df_dcpoMean %>% 
  left_join(df_controls, by = c("country", "year")) %>% 
  plm::pdata.frame(index = c("country", "year"))

ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")

@@

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoMeanAPSR)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoMeanAPSR)")
)

df_result_dcpoMeanAPSR <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))
})

result_dcpoMeanAPSR <- map(df_result_dcpoMeanAPSR, function(aResult) {
  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
    mutate(std.error = vcovHC_se(aResult))

names(result_dcpoMeanAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
```

```{r data-dcpoUncertainAPSR}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>%
    reformat_dcpo_output("theta") %>%
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>%
    plm::pdata.frame(index = c("country", "year"))
})

saveRDS(df_dcpoUncertainAPSR, here("data", "df_dcpoUncertainAPSR.rds"))
```

```{r dcpoUncertaintyAPSR}
## The same as in the previous chunk

ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")

### Different datasets

result_dcpoUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r visualizedAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

@@

```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

@@

```{r claassenFullUncertaintyAJPS}

load(here("data", "cls_ajps.rda")) # produced by cls_ajps_apsr_uncertain.R

result_clsUncertainFull <- map(ls_mod, function(aMod){ # reading a model
  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r dcpoFullUncertaintyAJPS}
load(here("data", "dcpo_ajps.rda")) # produced by dcpo_ajps_apsr_uncertain.R

ls_mod <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
    )
)

result_dcpoUncertainFull <- map(ls_mod, function(aMod){ # reading a model
  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}

@@

```{r claassenFullUncertaintyAPSR}

load(here("data", "cls_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R

result_clsFullUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))

```{r dcpoFullUncertaintyAPSR}
load(here("data", "dcpo_apsr.rda")) # produced by cls_ajps_apsr_uncertain.R

ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")

### Different datasets

###Duble check the dataset--------------
ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)

result_dcpoUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

```{r visualizedFullUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

@@

# Replication with Alternative Methods Accounting for Uncertainty
```{r  MocclaassenUncertaintyAJPS}
load("data/cls_ajps.rda")
df_cls <- purrr::map(1:900, function(anEntry) {
  cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ls_iv <- c("plm::lag(SupDem_trim, 1)",                         ##sumpdem_trim, our model did not use trim
           "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")
ls_method <- c("plm", "pgmm")
ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + 
              plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + 
              plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")

@@

df_dcpo <- purrr::map(1:900, function(anEntry) {
  dcpo_ajps[[anEntry]] %>% 
    mutate(theta_dem = ifelse(is.na(theta_trim),NA,theta_dem),
           theta_aut = ifelse(is.na(theta_trim),NA,theta_aut)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ls_iv <- c("plm::lag(theta_trim, 1)", 
           "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1)") 
ls_method <- c("plm", "pgmm")
ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)") 
ls_mod <- c(
  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
  glue(
    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
  )
)

>>>>

source(here("R", "tidy_pgmm.r"))
source(here("R", "moc_function.R")) 
source(here("R", "moc_summary.R")) 
source(here("R", "customFunctions.R"))

@@

supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
v_dem <- read.csv(here("data", "vdem15.csv"))    ######????????? why we need this one? for graph?  in the following analysis, we never use v_dem
sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

# produced by cls_ajps_apsr_uncertain.R and dcpo_ajps_apsr_uncertain.R
load(here("data", "cls_ajps.rda")) 
load(here("data", "dcpo_ajps.rda")) 
load(here("data", "cls_apsr.rda"))
load(here("data", "dcpo_apsr.rda"))

claassen_replication <- readRDS(here("data", "claassen_replication.rds")) %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here("data", "claassen_m5_theta.rda"))
load(here("data", "dem_mood_apsr.RData"))
load(here("data", "dcpo_input.rda"))
load(here("data", "dcpo_theta.rda"))
load(here("data", "dcpo_sigma.rda"))
load(here("data", "dcpo_ajps_rubin.rda"))
df_dcpoUncertainAPSR <- readRDS(here("data", "df_dcpoUncertainAPSR.rds"))

@@

```{r compare_n, eval = TRUE}
dcpo_input_raw1 <-
    read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>%
    filter(!(
        str_detect(survey, "army_wvs") &
            # WVS obs identified as problematic by Claassen
            ((country == "Albania" & year == 1998) |
                 (country == "Indonesia" &
                      (year == 2001 | year == 2006)) |
                 (country == "Iran" & year == 2000) |
                 (country == "Pakistan" &
                      (year == 1997 | year == 2001)) | # 1996 in Claassen
                 (country == "Vietnam" & year == 2001)
            ) |
            (str_detect(item, "strong_wvs") &
                 ((country == "Egypt" & year == 2012) |
                      (country == "Iran" &
                           (year == 2000 | year == 2007)) | # 2005 in Claassen
                      (country == "India") |
                      (country == "Pakistan" &
                           (year == 1997 | year == 2001)) | # 1996 in Claassen
                      (country == "Kyrgyzstan" &
                           (year == 2003 | year == 2011)) |
                      (country == "Romania" &
                           (year == 1998 | year == 2005 | year == 2012)) |
                      (country == "Vietnam" & year == 2001)
                 )) |
            (
                country %in% c(
                    "Puerto Rico",
                    "Northern Ireland",
                    "SrpSka Republic",
                    "Hong Kong SAR China"
                )
            )
    )) %>%
    with_min_yrs(2)

# if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
#   dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
#     read_csv(col_types = "cdcddcdc") %>% 
#     write_csv("data/supdem raw survey marginals.tab")
# }

@@

@@

```{r cls-pointAJPS}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

```{r cls-modelAJPS}

@@

ls_mod_ajpsCLS <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
    )
)

```{r cls-uncertainAJPSfull, eval=FALSE}
result_clsUncertainFull <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r dcpo-modelAJPS}
ls_iv <- c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")

@@

ls_mod_ajpsDCPO <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
    )
)
```

```{r dcpo-uncertainAJPSfull, eval=FALSE}
result_dcpoUncertainFull <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", eval=FALSE}

@@

```{r cls-pointAPSR}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

```{r cls-modelAPSR}
ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")

@@

ls_mod_apsrCLS <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = aData)")
)
```

```{r cls-uncertainAPSRfull, eval=FALSE}
result_clsFullUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))
```

```{r dcpo-modelAPSR}
ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")

@@

ls_mod_apsrDCPO <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)
```

```{r dcpo-uncertainAPSRfull, eval=FALSE}
result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=FALSE}

@@

@@

```{r cls-uncertainAJPSmain, eval=FALSE}
ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

df_cls <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(sd_control, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_clsUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r dcpo-uncertainAJPSmain, eval=FALSE}
df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
  .x[[.y]] %>%
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>%
    plm::pdata.frame(index = c("country", "year"))
}) # The code is to fit the embedded format of dcpo_ajps_rubin

result_dcpoUncertain <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
  mod_eval <- function(aData) eval(parse(text = aMod))

@@

```{r cls-undertainAPSRmain, eval=FALSE}
ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

result_clsUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

```{r dcpo-uncertainAPSRmain, eval=FALSE}
result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

# Replications of Full Pack of Models in Claassen 2020a,b

```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10}

```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}

@@

```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

@@

# Replication with Alternative Methods Accounting for Uncertainty
```{r MocclaassenUncertaintyAJPS}
load(here("data","cls_ajps.rda"))

df_cls <- purrr::map(1:900, function(anEntry) {
  cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ls_iv <- c("plm::lag(SupDem_trim, 1)",                         
           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") ##all use trim
ls_method <- c("plm", "pgmm")
ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + 
              plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + 
              plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")

@@

df_dcpo <- purrr::map(1:900, function(anEntry) {
  dcpo_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
    plm::pdata.frame(index = c("country", "year"))
})

ls_iv <- c("plm::lag(theta_trim, 1)", 
           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1)") #use trimed data
ls_method <- c("plm", "pgmm")
ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)") 
ls_mod <- c(
  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
  glue(
    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
  )
)
